---
title: "Alcohol vs Seat choice"
author: "Desmond Koutso"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row

## you choose to sit in??

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.  

$H_A$: The average number drinks is different between at least two rows.  



## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

From this plot, it is observed that the people sitting in the at the back consume more alcohol.\
The people at the front seat consume less alcohol, while the people in the middle are the next that consume more alcohol after the people at the back.

### get fancy

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

from the boxplot, the people at the back show an alcoholic consumption of 60.\
the people at the front seat show an alcohol consumption of 20.\
the people at the middle seat show an alcohol consumption of 35.

## Numerical Summarys

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The table shows the median of the people at the back is 4.  
The median of the people in front is 0.  
the median of the people at the middle is 1.  

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

Based on our inferential test carried out, the p-value is 0.000116.  
Due to the p-value being less than 0.05,we reject the null hypothesis.    


```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

from the plot above, the people at the middle-front are the only people that have have a 0 passing across them.


## Conclusions
the question was if there is a difference between the alcohol consumed between the row?  
my conclusion is there is a difference between the alcohol consumption the row.  
